---
title: "Music Group"
author: "Reuben Narad, Kelly Chu, Anika Mishra, Ruoxue Yan"
date: "5/20/2020"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE)
source("scripts/summary_info_script.R")
source("scripts/reuben_analysis.R")
source("scripts/world_2010s_analysis.R")
source("scripts/aggregate_table_script.R")
source("scripts/top50_country_bar.R")
```

This is our R markdown file

## Introduction

Our domain of interest is music. We visualized information about trends in the music industry to allow viewers to learn more about how their music preferences compare. Additionally, we hope to discover and showcase patterns in music that becomes popular.

For musicians, it is critical to understand what aspects of music lead to commercial success. Many factors, including speed, genre, dancability, and energy play a role in the likelihood that a song will be a "hit." This analysis can also be used to help a prospective musician make choices about the type of music to produce, if they wish to gain popularity. 

## Summary
There are `r summary$number_rows` rows in our dataset (Top 50 Spotify songs by each country), which provides a good range of information. Overall, `r summary$loudest_song` is the loudest song, and `r summary$song_highest_energy` is the song with the highest energy level. Knowing how a loud song and or high energy song sounds like will give insights to musicians on different song features. 
Songs from `r summary$max_danceability_country` have the highest average danceability level. Moreover, songs from `r summary$max_loudness_country` have the loudest volume. From the two values above, we can understand music characteristics certain countries have. All in all, these songs with extreme values help showcase the different music elements to the average viewer. 


## Aggregate Table by Genre

```{R echo=FALSE}
kable(aggregate_table(top_2010s), col.names = c("Genre","Popularity (0 to 100)", "BPM", "Energy","Dance-ability", "Liveliness") )
```

Organized by genre and sorted from greatest to least popularity score, this table contains the average data for each category. This table reveals that there are no clear patterns or correlations between these measurements and popularity. For example, beats per minute is relatively high on both ends of the popularity scale. Energy also seems patternless. However, the average measurements may indicate the general "recipe" for popular songs instead of the correlation amongst genres stats and popularity. 

## Charts

#### Country BPM Chart

Music tastes vary from country to country. While one country may prefer faster, more energetic songs, another may prefer slower, calmer songs. A musician may be interested to know what their country prefers. This chart shows the average speed and energy level of top 50 songs in various countries. To view which country each bar represents, hover over it.

A bar chart based on speed was chosen over a scatterplot based on speed and energy to more clearly juxtapose speed, the more important of the two variables. Energy level, a more ordinal type of measure, was encoded with color to simply show "high energy" and "low energy", rather than "exactly x amount of energy."

As seen in the chart, the majority of countries group around the 125 BPM area. However, there are clear outliers. Brazil has, on average, the fastest and highest energy music. In contrast, Indonesia has quite slow and calm music. One interesting point is the USA. Although the average BPM is roughly the average of the world, the energy level is the lowest of all the countries. Maybe it has to do with that **good ol' country twang**, or maybe it's Adelle. Regardless, the chart highlights that it's worth looking into.

```{r echo=FALSE}
chart_function(top_50_data)
```


#### Top Genres in the US from the Last Decade 

This pie chart was intended to show the breakdown of music trends over the past decade through the relationship between genre and popularity. Using angles and colors to highlight the quantitative information, this visual displays the range in popularity of music genres. A few genres were combined under broader genre names (ie. Iggy Azaelia from "Austrailian Hip Hop" to "Hip Hop".) 

This graph shows that dance pop and pop fittingly dominated the genres of the most popular songs in the 2010s. Following pop, EDM and hip hop were the next most popular respectively. Although having the third greatest percentage, misc. indicates the total number of songs of genres that had fewer than 4 total hit songs over the given years. Adele in her stand alone genre, "British Soul", had more popular songs in the 2010s than four other listed genres.

```{r, echo=FALSE}
top2010_pie_chart(world_top2010)
```


#### Number of countries a genre is the most common, by year
This bar chart looks at the each "Top Genre", and finds the number of countries
where that genre was the top genre, based on the year specified by the user. This
could allow a user to see how many countries their favorite genre is popular in.
For the year 2018, alternative r&b was the most popular, being the most common
genre for the top50 datasets in 7 countries. This means that that genre is far
more popular than something like 'anime rock'. This data visualization could help
artists who are creating or writing new music, or who are hoping to break into
the music industry to see what their chances of success are based on genre and top50
charts over several decades.

```{r, echo=FALSE}
interactive_bar(2018)
```

